---
title: "shoppingwords: A Guide to Using the Package"
output: rmarkdown::html_vignette
date: "`r Sys.Date()`"
vignette: >
  %\VignetteEncoding{UTF-8}
  %\VignetteIndexEntry{shoppingwords: A Guide to Using the Package}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r}
#| include = FALSE
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Overview

The shoppingwords package provides functions for loading, normalizing, and analyzing textual data, primarily from user reviews. This tutorial covers dataset loading from RDA formats, as well as text normalization by removing stopwords, extracting phrases, and includes labeled polarity datasets.

The goal of this R package is to provide a structured dataset and analytical tools for understanding the relationship between user ratings and emotional sentiment in consumer reviews. This package will serve as a valuable resource for text mining, sentiment analysis, and behavioral research, enabling users to explore patterns in high ratings that are associated with negative emotions.


# Installation

Before using shoppingwords, install it from CRAN via:

```{r}
#| eval: false
install.packages("shoppingwords")
```

or install the development version from GitHub via:

```{r}
#| eval: false
pak::pak("bkanx/shoppingwords")
```

# Packages

For this vignette we will use the shoppingwords, knitr, tibble, and dplyr packages:

```{r}
#| message: false
library(shoppingwords)
library(knitr)
library(tibble)
library(dplyr)
```

# Loading Datasets

The **shoppingwords** package provides several datasets useful for text processing and analysis. This section introduces the datasets stored in the `data/` folder, explaining their contents and showing how to load them into R.


## Available Datasets

The following datasets are included in the package:

| Dataset Name                 | Format  | Description |
|------------------------------|--------|-------------|
| `corrected_words.rda`        | RDA    | A collection of corrected words in Turkish for text normalization. |
| `phrases.rda`                | RDA    | A data containing predefined Turkish phrases for analysis. |
| `reviews.rda`                | RDA    | Turkish raw review data for sentiment analysis and NLP tasks. |
| `stopwords_tr.rda`           | RDA   | A list of Turkish stopwords including shopping-based terms for text preprocessing. |
| `testdata.rda`               | RDA   | Sample test data including sentence-based polarity for further NLP tasks (In Turkish). |


The review_**`reviews.rda`** data is the core component of the shoppingwords package, designed for text analysis, sentiment scoring, or NLP tasks (e.g., customer feedback mining). The **`get()`** function provides a convenient way to load datasets by specifying their name.

### Loading Reviews Dataset

The package stores **`reviews.rda`** data in an optimized RDA format for fast access. The **`get()`** function loads the main data of product reviews from an RDA file stored within the package. 

#### **Data Structure**
| Column   | Description |
|----------|-------------|
| `rating` | Numerical rating (1-5) from user reviews. |
| `comment`   | Review content, including product opinions. |
|


```{r}
#| message: false
# Load reviews from RDA
reviews <- get("reviews")
str(reviews)

# English Explanation
#>  $ comment: chr  “Very good, true to size.” “Very good, you can buy one size smaller.” “Very good, true to size.” "Really.
```


All other functions (e.g., stopword removal, phrase analysis) are optimized for the **`reviews.rda`** data. It enables analysis of Turkish e-commerce reviews (e.g., rating scores, common complaints).

To demonstrate a practical analytical use case for the preprocessed review data and how the package's functions work together in a real analysis workflow is given in the Examples. The example calculates if longer reviews correlate with higher/lower ratings - a common business question in review analysis.


```{r}
#| message: false
# Preprocess reviews  
cleaned_reviews <- match_stopwords(reviews)  # Remove stopwords  
head(cleaned_reviews, 3)
```

```{r}
# English Translation
#>   rating                             comment                 cleaned_text
#> 1      5                 Very good, perfect fit                     fit
#> 2      5 Very nice, a size smaller can be taken nice size smaller can be taken
#> 3      5                 Very nice, fits well                    nice

```


```{r}
# Analyze sentiment vs. ratings  
library(dplyr)  
cleaned_reviews |>    
  group_by(rating) |>   
  summarise(avg_text_length = mean(nchar(cleaned_text)))  
```



### Loading Corrected Words

The `get()` function allows users to load a predefined data of corrected words from within the package. The function restructures **corrected_words.rda`** data into a **long format** for easier text analysis. It is a restructured spelling variants or slang (e.g., "fiyattt" → "fiyat") for further text analysis. The **˜corrected_words.rda˜** data contains 10,137 pairs of commonly misspelled Turkish words and their corrected versions, particularly useful for normalizing shopping-related text.


```{r}
#| message: false
#| eval: false
# Load corrected words from RDA
get("corrected_words")
```


```{r}
#| message: false
#| echo: false
# Load corrected words from RDA
get("corrected_words")[c(28,44,58),]
```


```{r}
# English Translation
#>   word       corrected 
#>   <chr>      <chr>     
#> 1 dıdn't write   didn't write  
#> 2 probabl        probably  
#> 3 w.ant.ed       wanted  

```


### Loading Stopwords

The `get()` function also retrieves a predefined list of 92 stopwords from a RDA file stored within the package. These stopwords are commonly found in Turkish shopping-related text and are useful for text preprocessing and analysis. **`stopwords_tr`** is a data specific to Turkish stopwords.

```{r}
#| message: false
#| eval: false
# Load Turkish shopping-based stopwords from RDA
get("stopwords_tr")
```

```{r}
#| message: false
#| echo: false
# Load Turkish shopping-based stopwords from RDA
get("stopwords_tr")[37:39,]
```


**`stopwords-iso`** is a standardized multilingual stopword collection, including Turkish but potentially with broader coverage.

```{r}
#| message: false
#| eval: false
# or load a few stopwords from stopwords-iso 
stopwords::stopwords("tr", source = "stopwords-iso") |> head()
```

```{r}
#| message: false
#| echo: false
# or load a few stopwords from stopwords-iso 
stopwords::stopwords("tr", source = "stopwords-iso") |> head()
```

```{r}
# English Translation
#> [1] "I wonder"   "perhaps"    "clearly"    "frankly"    "thoroughly"
#> [6] "almost"  
```


Using both datasets reduces the risk of missing critical stopwords that could skew sentiment or topic modeling results.


### Loading Phrases

The `get()` function also retrieves predefined shopping-related phrases from the **`phrases.rda`** file stored within the package. 

```{r}
#| message: false
#| eval: false
# Load predefined Turkish shopping-based phrases
get("phrases") 
```

```{r}
#| message: false
#| echo: false
get("phrases")[5:9,]
```

```{r}
# English Translation
#> [1] "So it appears at the top"            "I gave 5 stars so it appears at the top"
#> [3] "so it appears at the top"            "so it appears at the top five"            
#> [5] "Do not buy at all"

```


These phrases assist in text processing, linguistic analysis, and Natural Language Processing (NLP) applications, making it easier to analyze customer behavior and responses.


### Cleaning text

The `match_stopwords()` is a function that processes user reviews by removing predefined stopwords while preserving the original rating scores. It takes a dataframe with "comment" and "rating" columns, cleans each review by filtering out stopwords from both custom stopword lists and stopwords-iso, and returns a dataframe with an additional "cleaned_text" column for further analysis. This function helps in text normalization for sentiment analysis and rating-based insights.


```{r}
#| message: false
#| eval: false

reviews_sample <- tibble(
    comment = c("Bu ürün gerçekten çok iyi ancak fiyatı sadece yüksek gibi", 
                "Fiyat çok pahalı ama kaliteli iyi"), 
    rating = c(4.5, 3.0)
)
cleaned_sample <- match_stopwords(reviews_sample) # expects a data frame, not a name in quotes
```

```{r}
# English translation
# comment = c("This product is really good, but the price seems just high", 
#            "The price is very expensive, but it's high-quality and good")
```


```{r}
#| echo: false
#| message: false
reviews_sample <- tibble(
    rating = c(4.5, 3.0),
    comment = c("Bu ürün gerçekten çok iyi ancak fiyatı sadece yüksek gibi", 
                "Fiyat çok pahalı ama kaliteli iyi")
    )
cleaned_sample <- match_stopwords(reviews_sample)
kable(cleaned_sample) 
```

Alternatively, users might pass the selected reviews to match_stopwords():

```{r}
#| message: false
# or using a few reviews from raw data 
data("reviews", package = "shoppingwords")
reviews_sample <- reviews[c(115296,110425),]
reviews_sample <-  match_stopwords(reviews_sample)
kable(reviews_sample)
```


| rating  | comment                                                                                      | cleaned_text                                                      |
|---------|----------------------------------------------------------------------------------------------|------------------------------------------------------------------|
| 115296  | I gave 5 stars so it appears at the top. On my second wear, despite not washing, the back stitches came undone and burst. | appears at the top 5 stars I give 2nd wear despite not washing back stitches opened burst |
| 110425  | I gave 5 stars so it appears at the top. They sent two tops, which is very careless behavior. I'm dealing with returns. | appears at the top 5 stars I gave. sent two tops careless behavior. dealing with return |



## Sentiment Polarity Data

The `shoppingwords` package also includes a **testdata.rda** data for text mining and NLP tasks. This data contains user-generated reviews labeled as **positive (`p`)** or **negative (`n`)**, being different than reviews data and making it useful for training models in sentiment classification.

#### **Data Structure**
| Column   | Description |
|----------|-------------|
| `rating` | Numerical rating (1-5) from user reviews. |
| `text`   | Review content, including product opinions. |
| `emotion` | Sentiment label (`p`: positive, `n`: negative). |

### **Loading the testdata**


```{r}
#| message: false
#| echo: false
# Load polarity dataset
data("testdata", package = "shoppingwords")
head(testdata, 3)
```
```{r}
#>   rating
#> 1      5
#> 2      5
#> 3      5
#>  text
#> 1 Definitely buy it! No need to spend so much on expensive brands; the fit looks incredibly good.  
#> 2 If I could give 10 stars, I would. Super!  
#> 3 The product deserves 5 stars. I bought both M and L sizes, and they fit the same. I really liked it.
#>   emotion
#> 1       p
#> 2       p
#> 3       p
```


Once loaded, users can analyze the data:

```{r}
#| message: false
#| 
# Count positive vs. negative reviews
testdata |> 
  count(emotion, sort = TRUE)
```

Summarizing the occurrences of rating and emotion in relation to negative and positive reviews is insightful. Notably, 204 reviews contain negative expressions even though they have been assigned a rating of 5, out of a total of 2244 reviews.

```{r}
# Occurences of rating and emotion
testdata |> 
  count(rating, emotion, sort = TRUE) |> 
  arrange(desc(rating))
```

The testdata can be used in various ways such as capturing the negative expressions or predciting sentence-level polarity using the **`reviews.rda`** data. 


# References
Kan-Kilinc, B., Cetinkaya-Rundel, M. & Rundel, C. (2023). shoppingwords: Text Processing Tools for Turkish E-Commerce Data. R package version 0.1.0.
Available at: https://github.com/bkanx/shoppingwords


Wickham, H., François, R., Henry, L., Müller, K., & Vaughan, D. (2023). dplyr: A Grammar of Data Manipulation. R package version 1.1.2.
URL: https://CRAN.R-project.org/package=dplyr


Xie, Y. (2023). knitr: A General-Purpose Package for Dynamic Report Generation in R. R package version 1.43.
URL: https://yihui.org/knitr/


Zhu, H. (2021). kableExtra: Construct Complex Table with 'kable' and Pipe Syntax. R package version 1.3.4.
URL: https://CRAN.R-project.org/package=kableExtra


Müller, K., & Wickham, H. (2023). tibble: Simple Data Frames. R package version 3.2.1.
URL: https://CRAN.R-project.org/package=tibble


Benoit, K., Muhr, D., & Watanabe, K. (2021). stopwords: Multilingual Stopword Lists. R package version 2.3.
URL: https://CRAN.R-project.org/package=stopwords


Csárdi, G. (2022). pak: A Fresh Approach to R Package Installation. R package version 0.3.1.
URL: https://CRAN.R-project.org/package=pak


