---
title: "shoppingwords: A Guide to Using the Package"
output: rmarkdown::html_vignette
date: "`r Sys.Date()`"
vignette: >
  %\VignetteEncoding{UTF-8}
  %\VignetteIndexEntry{shoppingwords: A Guide to Using the Package}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r}
#| include = FALSE
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Overview

This tutorial introduces the shoppingwords package, designed to simplify text processing and sentiment analysis for consumer reviews. The shoppingwords package facilitates datasets loading from RDA formats and provides stopword removal and phrase extraction. It also includes labeled polarity datasets for sentiment analysis.

The goal of this R package is to offer a structured dataset and analytical tools for exploring the relationship between user ratings and emotional sentiment in consumer reviews. It serves as a valuable resource for text mining, sentiment analysis, and behavioral research, helping users identify patterns where high ratings may be linked to negative emotion.


# Installation

Before using shoppingwords, install it from CRAN via:

```{r}
#| eval: false
install.packages("shoppingwords")
```

or install the development version from GitHub via:

```{r}
#| eval: false
pak::pak("bkanx/shoppingwords")
```

# Packages

For this vignette we will use the shoppingwords, knitr, tibble, and dplyr packages:

```{r}
#| message: false
library(shoppingwords)
library(knitr)
library(tibble)
library(dplyr)
```

# Loading Datasets

The **shoppingwords** package provides several datasets useful for text processing and analysis. This section introduces the datasets stored in the `data/` folder, explaining their contents and showing how to load them into R.


## Available Datasets

The following datasets included in the package are given in Table 1:

| Dataset Name                 | Format  | Description |
|------------------------------|--------|-------------|
| `reviews.rda`                | RDA    | Turkish raw review data for sentiment analysis and NLP tasks. |
| `stopwords_tr.rda`           | RDA   | A list of Turkish stopwords including shopping-based terms for text preprocessing. |
| `phrases.rda`                | RDA    | A data containing predefined Turkish phrases for analysis. |
| `testdata.rda`               | RDA   | Sample test data including sentence-based polarity for further NLP tasks (In Turkish). |
_Table 1: Overview of the datasets._

The review_**`reviews.rda`** data is the core component of the shoppingwords package, designed for text analysis, sentiment scoring, or NLP tasks (e.g., customer feedback mining). The **`get()`** function provides a convenient way to load datasets by specifying their name.

### Loading Reviews Dataset

The package stores **`reviews.rda`** data in an optimized RDA format for fast access. The **`get()`** function loads the main data of product reviews from an RDA file stored within the package. Table 2 provides a structured overview of the **`reviews.rda`** dataset, detailing user ratings, review content, and unique identifiers.

#### **Data Structure**
| Column   | Description |
|----------|-------------|
| `rating` | Numerical rating (1-5) from user reviews. |
| `comment`   | Review content, including product opinions. |
| `id` | Unique ID|
_Table 2: Overview of the `**reviews.rda`** dataset._


```{r}
#| message: false
# Load reviews from RDA
reviews <- get("reviews")
str(reviews)

# English Explanation
#>  $ comment: chr  “Very good, true to size.” “Very good, you can buy one size smaller.” “Very good, true to size.” "Really.
```


The **`reviews.rda`** data enables the analysis of Turkish e-commerce reviews (e.g., rating scores, common complaints).
The earliest review is from April 16, 2022. The latest review is from June 11, 2025. The dataset spans over 3 years, capturing reviews from users, including 260,308 rows, in customer feedback. The examples have been translated from Turkish, as the dataset contains Turkish-language reviews.


### Loading Stopwords

The `get()` function also retrieves a predefined list of stopwords from a RDA file stored within the package. These stopwords are commonly found in Turkish shopping-related text and are useful for text preprocessing and analysis. **`stopwords_tr`** is a data specific to Turkish stopwords.

```{r}
#| message: false
#| eval: false
# Load Turkish shopping-based stopwords from RDA
get("stopwords_tr")
```

```{r}
#| message: false
#| echo: false
# Load Turkish shopping-based stopwords from RDA
get("stopwords_tr")[37:39,]
```


**`stopwords-iso`** is a standardized multilingual stopword collection, including Turkish but potentially with broader coverage.

```{r}
#| message: false
#| eval: false
# or load a few stopwords from stopwords-iso 
stopwords::stopwords("tr", source = "stopwords-iso") |> head()
```

```{r}
#| message: false
#| echo: false
# or load a few stopwords from stopwords-iso 
stopwords::stopwords("tr", source = "stopwords-iso") |> head(5)
```

```{r}
# English Translation
#> [1] "I wonder"   "perhaps"    "clearly"    "frankly"    "thoroughly"
```


Using both datasets reduces the risk of missing critical stopwords that could skew sentiment or topic modeling results.


### Loading Phrases

The `get()` function also retrieves predefined shopping-related phrases from the **`phrases.rda`** file stored within the package. 

```{r}
#| message: false
#| eval: false
# Load predefined Turkish shopping-based phrases
get("phrases") 
```

```{r}
#| message: false
#| echo: false
get("phrases")[7:8,]
```

```{r}
# English Translation
#> [1] "so it appears at the top"
#> [2] "so it appears at the top five" 

```


These phrases assist in text processing, linguistic analysis, and Natural Language Processing (NLP) applications, making it easier to analyze customer behavior and responses.


### Cleaning Text

The `match_stopwords()` is a function that processes user reviews by removing predefined stopwords while preserving the original rating scores. It takes a dataframe with "comment" and "rating" columns, cleans each review by filtering out stopwords from both custom stopword lists and stopwords-iso, and returns a dataframe with an additional "cleaned_text" column for further analysis. This function helps in text normalization for sentiment analysis and rating-based insights.


To demonstrate a practical analytical use case for the preprocessed review data and how the package's function work together in a real analysis workflow is given in the examples. The example calculates if longer reviews correlate with higher/lower ratings. 


```{r}
# Analyze sentiment vs. ratings  
library(dplyr)  
cleaned_reviews <- match_stopwords(reviews)  # Remove stopwords 
cleaned_reviews |>    
  group_by(rating) |>   
  summarise(avg_text_length = mean(nchar(cleaned_text)))  
```


```{r}
#| message: false
reviews_sample <- tibble(
    comment = c("Bu ürün gerçekten çok iyi ancak fiyatı sadece yüksek gibi", 
                "Fiyat çok pahalı ama kaliteli iyi"), 
    rating = c(4.5, 3.0)
)
cleaned_sample <- match_stopwords(reviews_sample) # expects a data frame, not a name in quotes
```

The function can be applied to another sample dataset as well.

```{r}
#| echo: false
#| message: false
reviews_sample <- tibble(
    rating = c(4.5, 3.0),
    comment = c("Bu ürün xs ancak fiyatı yüksek gibi", 
                "Fiyat çok pahalı değil kaliteli iyi")
    )
cleaned_sample <- match_stopwords(reviews_sample)
cleaned_sample
```

```{r}
# English translation
# comment                                                    cleaned_text
# "This product is xs but seems realy expensive"            "the product price high" 
# "The price is not very expensive it's high-quality good"  "the price expensive high-quality"
```



## Sentiment Polarity Data

The `shoppingwords` package also includes a **testdata.rda** data for text mining and NLP tasks. This data contains user-generated reviews labeled as **positive (`p`)** or **negative (`n`)**, being different than reviews data and making it useful for training models in sentiment classification (See Table 3).

#### **Data Structure**
| Column   | Description |
|----------|-------------|
| `rating` | Numerical rating (1-5) from user reviews. |
| `text`   | Review content, including product opinions. |
| `emotion` | Sentiment label (`p`: positive, `n`: negative). |
_Table 3: Overview of the **`testdata.rda`** dataset._

### **Loading the testdata**
Below is a preview of the test dataset, which includes customer ratings, review text, and sentiment labels. Each row represents user feedback, providing insights into product perception and satisfaction.

```{r}
#| message: false
#| echo: false
# Load polarity dataset
data("testdata", package = "shoppingwords")
head(testdata, 3)
```
```{r}
# English translation
#>   rating
#> 1      5
#> 2      5
#> 3      5
#>  text
#> 1 Definitely buy it! No need to spend so much on expensive brands; the fit looks incredibly good.  
#> 2 If I could give 10 stars, I would. Super!  
#> 3 The product deserves 5 stars. I bought both M and L sizes, and they fit the same. I really liked it.
#>   emotion
#> 1       p
#> 2       p
#> 3       p
```

Once loaded, users can analyze the data:

```{r}
#| message: false
#| 
# Count positive vs. negative reviews
testdata |> 
  count(emotion, sort = TRUE)
```

Summarizing the occurrences of rating and emotion in relation to negative and positive reviews is insightful. Notably, 204 reviews contain negative expressions even though they have been assigned a rating of 5, out of a total of 2244 reviews.

```{r}
# Occurences of rating and emotion
testdata |> 
  count(rating, emotion, sort = TRUE) |> 
  arrange(desc(rating))
```

The testdata can be used in various ways such as capturing the negative expressions or predciting sentence-level polarity using the **`reviews.rda`** data. 


# References
Kan-Kilinc, B., Cetinkaya-Rundel, M. & Rundel, C. (2025). shoppingwords: Text Processing Tools for Turkish E-Commerce Data. R package version 0.1.0.
Available at: https://github.com/bkanx/shoppingwords


Wickham, H., François, R., Henry, L., Müller, K., & Vaughan, D. (2023). dplyr: A Grammar of Data Manipulation. R package version 1.1.2.
URL: https://CRAN.R-project.org/package=dplyr


Xie, Y. (2023). knitr: A General-Purpose Package for Dynamic Report Generation in R. R package version 1.43.
URL: https://yihui.org/knitr/


Müller, K., & Wickham, H. (2023). tibble: Simple Data Frames. R package version 3.2.1.
URL: https://CRAN.R-project.org/package=tibble


Benoit, K., Muhr, D., & Watanabe, K. (2021). stopwords: Multilingual Stopword Lists. R package version 2.3.
URL: https://CRAN.R-project.org/package=stopwords


Csárdi, G. (2022). pak: A Fresh Approach to R Package Installation. R package version 0.3.1.
URL: https://CRAN.R-project.org/package=pak


