---
title: "shoppingwords: A Guide to Using the Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{shoppingwords_tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

### Overview

The shoppingwords package provides functions for loading, normalizing, and analyzing textual data, primarily from reviews. This tutorial will cover:

 ### Installation
Before using shoppingwords, install it from GitHub:

```{r, message=FALSE}
devtools::install_github("bkanx/shoppingwords")
library(shoppingwords)
```

If submitting to CRAN, users can install it via:

```{r, eval=FALSE}
install.packages("shoppingwords")
```


### Loading datasets
The package stores review data in an optimized RDS format for fast access. Load it using:

```{r}
reviews_data <- load_reviews()
```

Returns: A tibble with review IDs and text content. Check the first few rows:

```{r}
library(knitr)
kable(head(reviews_data))
```

### Cleaning text

match_stopwords() is a function that processes user reviews by removing predefined stopwords while preserving the original rating scores. It takes a dataframe with "comment" and "rating" columns, cleans each review by filtering out stopwords from both custom stopword lists and stopwords-iso, and returns a dataframe with an additional "cleaned_text" column for further analysis. This function helps in text normalization for sentiment analysis and rating-based insights.

```{r, message=FALSE}
# Example
library(tibble)
reviews_sample <- tibble(
    comment = c("Bu ürün gerçekten çok iyi ancak fiyatı sadece yüksek gibi", 
                "Fiyat çok pahalı ama kaliteli iyi"), 
    rating = c(4.5, 3.0)
)

(cleaned_sample <- kable(match_stopwords(reviews_sample)))
```



